\documentclass[a4paper, amsfonts, amssymb, amsmath, reprint, showkeys, nofootinbib, twoside]{revtex4-1}
\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage[colorinlistoftodos, color=green!40, prependcaption]{todonotes}
\input{preamble}
\usepackage[pdftex, pdftitle={Article}, pdfauthor={Author}]{hyperref} % For hyperlinks in the PDF
%\setlength{\marginparwidth}{2.5cm}
%\usepackage{biblatex}
%\addbibresource{Reference.bib}
\bibliographystyle{apsrev4-1}
\begin{document}
\title{Hubble constant "in tension"}

\author{noble-alligators}
    \email[Correspondence email address: ]{email@institution.com}% Your name
    \affiliation{Physics Department, University  of Rochester.}

\date{\today} % Leave empty to omit a date

\begin{abstract}
Abstract
\end{abstract}

\keywords{first keyword, second keyword, third keyword}


\maketitle

\input{sections/background.tex}  %I believe leaving the sections in separate files is more organized, change it if you desire 
\input{sections/methodology.tex}
\input{sections/results.tex}
\input{sections/conclusion.tex}
\input{sections/acknowledgements.tex}

\begin{thebibliography}{4}
\bibitem{Griffiths}
D. J. Griffiths,
\textit{Introduction to Electrodynamics}
(Cambridge University Press, Cambridge, 2017).

\bibitem{Plank2018}
Aghanim, N., Akrami, Y., Ashdown, M., Aumont, J., Baccigalupi, C., Ballardini, M., Banday, A. J., Barreiro, R. B., Bartolo, N., Basak, S., Battye, R., Benabed, K., Bernard, J.-P., Bersanelli, M., Bielewicz, P., Bock, J. J., Bond, J. R., Borrill, J., Bouchet, F. R., … Zonca, A. (2020). Planck 2018 results. VI. Cosmological parameters. Astronomy &amp; Astrophysics, 641. https://doi.org/10.1051/0004-6361/201833910 .

\bibitem{Feynman}
R. P. Feynman, R. B. Leighton and M. Sands,
\textit{Lições de Física de Feynman}
(Editora Bookman, Porto Alegre, 2008).

\bibitem{Jackson-CE}
J. D. Jackson,
\textit{Classical Electrodynamics}
(John Wiley \& Sons, Danvers, 1999).
\end{thebibliography}

\appendix*
\input{sections/appendix1.tex}

\end{document}
